Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-26 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
then $\rho'$ is close to $\rho$. Conversely, if $\rho'$ is close
to $\rho$, $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
by the following lemma.

\begin{lemma}Given a $d$-dimensional Hilbert space with the set
of all projectors\nb$\events$, and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For two mixed state\nb$\rho$ and $\rho'$, if the following conditions
holds.
\begin{itemize}
\item Let $\delta=\min_{x\in\left(0,1\right)}\left\{ \max\iota\left(x\right)-x,x-\min\iota\left(x\right)\right\} $.
In another word, if $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
\item $\left\Vert \rho-\rho'\right\Vert \le d\delta$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
\end{itemize}
Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}

\begin{proof}Since
\begin{equation}
d\delta\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
\end{equation}
we have
\begin{equation}
d\delta\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
\end{equation}
for all normalized pure state\nb$\ket{\psi}$.

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
Therefore, for any mixed state\nb$\rho$ such that .\end{example}

>>>>

Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
then $\rho'$ is close to $\rho$. Conversely, if $\rho'$ is close
to $\rho$, $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
Before we introduce the lemma, we start the following definition.

\begin{definition}A mixed state\nb$\rho$ is called totally mixed
if it satisfies the following conditions.
\begin{itemize}
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
\end{itemize}
\end{definition}

For example, any pure state is not totally mixed, and $\mathbb{1}/3$
is a totally mixed over a three-dimensional Hilbert space.

\begin{lemma}Given a $d$-dimensional Hilbert space with the set
of all projectors\nb$\events$, and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For two mixed state\nb$\rho$ and $\rho'$, if the following conditions
holds.
\begin{itemize}
\item Let $\delta=\min_{x\in\left(0,1\right)}\left\{ \max\iota\left(x\right)-x,x-\min\iota\left(x\right)\right\} $.
In another word, if $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
\item $\left\Vert \rho-\rho'\right\Vert \le\delta/d$.
\item $\rho$ is a totally mixed.
\end{itemize}
Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}

\begin{proof}Since
\begin{equation}
\frac{\delta}{d}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
\end{equation}
we have
\begin{equation}
\frac{\delta}{d}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
\end{equation}
for all normalized pure state\nb$\ket{\psi}$.

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le\left(4dn\right)^{-1}$, then
$\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
\end{example}
